TBD

### 2016-09-09 paper/paper.tex
write running example

\usepackage{algorithm}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
\usepackage[justification=centering]{caption}
\usepackage{stmaryrd}
\usepackage{hhline}
\usepackage{pifont}
\usepackage{longtable}
\usepackage{afterpage}
\usepackage{wasysym}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Overview}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Running Example}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Program Synthesis}

>>>>

\usepackage{algorithm}
\usepackage{amsfonts}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
\usepackage[justification=centering]{caption}
\usepackage{stmaryrd}
\usepackage{hhline}
\usepackage{pifont}
\usepackage{longtable}
\usepackage{afterpage}
\usepackage{wasysym}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Overview}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Running Example}

A classical cruise control example is extracted from the literature~\cite{Astrom08}, where the discrete plant model (with time step of $0.2$s) is represented by the following z-expression:

\begin{equation}
\label{Eq:running-example-plant}
P\left(z\right) := \frac{0.0264}{z-0.9998}.
\end{equation}

Using an optimization tool, Wang {\it et al.}~\cite{DBLP:conf/hybrid/WangGRJF16} design a high-performance controller, which is characterized by the following z-expression:

\begin{equation}
\label{Eq:running-example-controller}
C\left(z\right) := \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
\end{equation}

The authors claim that this controller $C(z)$ is extremely stable for the discrete plant model $P(z)$. However, if implementation aspects are considered during verification, this controller becomes unstable. To properly implement $C(z)$, there is a function $FWL[\cdot]:\mathbb{R}^{k+l+2}\rightarrow Q[\mathbb{R}^{k+l+2}]$, which applies FWL effects to the controller $C(z)$, where $Q[\mathbb{R}]$ represents the quantized set of representable real numbers in the chosen implementation format $<k,l>$ ($k$ is the number of bits of the integer part and $l$ is the number of bits of the fractional part).

For this particular example, the actual implementation of $C(z)$ using $<3,16>$ implementation format can be represented by the following z-expression:

\begin{equation}
\label{Eq:running-example-controller-quantized}
C_{q}\left(z\right) := \frac{2.7199859619140625z^2 - 4.1529998779296875z + 1.89599609375}{z^2 - 1.843994140625z + 0.8495941162109375},
\end{equation}

\noindent which makes the system unstable in closed-loop using series loop configuration.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Program Synthesis}
